Exploring the linear separablity of syntactic and semantic information in BERT embeddings

### 2022-06-09 paper/paper.tex
adding table of descritpion

%Summarize Main findings

This is where our results will go.

\begin{table*}[h]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Embedding} & \textbf{Directions Removed} & \textbf{CCG Tagging} &\textbf{Semantic Labeling} \\
    \hline
    Original & 0 & $84.75\%$ & $88.56\%$ \\
    \hline

    Rand($|v_{nosem}|$) & 77 & $84.06\%$ & $87.71\%$ \\
    Rand($|v_{nosyn}|$) & 159 & $82.26\%$ & $87.57\%$ \\
    Rand($|v_{syn-sem}|$) & 81 & p$83.11\%$ & $87.61\%$ \\
    Rand($|v_{sem-syn}|$) & 161 & $82.46\%$ & $86.04\%$ \\
    Rand($|v_{syn*sem}|$) & 0 & p$\%$ & p$\%$ \\
    Rand($|v_{sem*syn}|$) & 0 & p$\%$ & p$\%$ \\
    \hline
    $v_{nosem}$ & 77 & $27.93\%$ & $17.28\%$ \\
    $v_{nosyn}$ & 159 & $23.76\%$ & $49.43\%$ \\
    $v_{syn-sem}$ & 81 & $34.24\%$ & $33.91\%$ \\
    $v_{sem-syn}$ & 161 & $26.96\%$ & $50.21\%$ \\
    $v_{syn*sem}$ & 0 & p$\%$ & p$\%$ \\
    $v_{sem*syn}$ & 0 & p$\%$ & p$\%$ \\
    \hline
    \hline
    \end{tabular}
    \caption{\label{role description} Description of how to read results
    }
    \end{table*}

@@

>>>>

We first probe our tasks on the original embeddings, and linear classifers can successfully predict both CCG tags and semantics tags as resulted in table \ref{role description}. Then we apply INLP method to the linear classifers to derive guarding matrices $P_{syn}$ and $P_{sem}$ which will project the embeddings to the nullspace of syntactic space and semantic space respectively. With some linear tranformation with the original embeddings and the guarding matrices, we are able to extract the embeddings described in table \ref{description}. 
\begin{table}[ht]
    \centering
    \begin{tabular}{p{4cm}p{3cm}}
        expression & description\\ \hline 
        $v_{orig}$ & Original BERT embeddings  \\
        $v_{nosem} = P_{sem} v_{orig}$ & Gained after INLP with semantics task \\
        $v_{nosyn}= P_{syn} v_{orig}$ & Gained after INLP with syntactic task \\
        $v_{sem} = v_{orig}-v_{no_sem}$ & Semantics representation \\
        $v_{syn} = v_{orig}-v_{no_syn}$ & Syntactic representation \\
        $v_{syn-sem} = P_{sem} v_{syn}$ &Contains syntactic features only \\
        $v_{sem-syn} = P_{syn} v_{sem}$ &Contains semantic features only \\
        $v_{syn*sem} = \langle v_{syn}, v_{sem} \rangle \cdot \frac{v_{syn}}{\|v_{sem}\|}$ & Syntactic representations projected on semantic space\\
        $v_{sem*syn} = \langle v_{syn}, v_{sem} \rangle \cdot \frac{v_{syn}}{\|v_{syn}\|}$ & Semantics representations projected on semantic space\\

        \hline
    \end{tabular}
    \caption{\label{description} Description of Embeddings
    }
\end{table}

To further compare the impact of INLP, we

\begin{table*}[h]
    \centering
    \begin{tabular}{llll}
    \hline
    \textbf{Embedding} & \textbf{Directions Removed} & \textbf{CCG Tagging} &\textbf{Semantic Tagging} \\
    \hline
    $v_{orig}$ & 0 & $84.75\%$ & $88.56\%$ \\
    \hline

    Rand($|v_{nosem}|$) & 77 & $84.06\%$ & $87.71\%$ \\
    Rand($|v_{nosyn}|$) & 159 & $82.26\%$ & $87.57\%$ \\
    Rand($|v_{syn-sem}|$) & 81 & p$83.11\%$ & $87.61\%$ \\
    Rand($|v_{sem-syn}|$) & 161 & $82.46\%$ & $86.04\%$ \\
    Rand($|v_{syn*sem}|$) & 0 & p$\%$ & p$\%$ \\
    Rand($|v_{sem*syn}|$) & 0 & p$\%$ & p$\%$ \\
    \hline
    $v_{nosem}$ & 77 & $27.93\%$ & $17.28\%$ \\
    $v_{nosyn}$ & 159 & $23.76\%$ & $49.43\%$ \\
    $v_{syn-sem}$ & 81 & $34.24\%$ & $33.91\%$ \\
    $v_{sem-syn}$ & 161 & $26.96\%$ & $50.21\%$ \\
    $v_{syn*sem}$ & 0 & p$\%$ & p$\%$ \\
    $v_{sem*syn}$ & 0 & p$\%$ & p$\%$ \\
    \hline
    \hline
    \end{tabular}
    \caption{\label{role description} Experiment Result of different Embeddings
    }
    \end{table*}

@@

The INLP methods
